---
title: "hydromulch-greenhouse"
author: "Jpukabeals"
date: "7/5/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# this code will automatically install the needed packages
if (!require("pacman"))
  install.packages("pacman")
pacman::p_load(
  tidyverse,
  lme4,
  multcomp,
  multcompView,
  googlesheets4,
  googledrive,
  lubridate,
  rstatix,
  #for is_outlier/is_extreme
  plotrix,
  #for std.error
  knitr,
  #for kable function
  drc
)
options(scipen = 999)
options(digits = 2)
```

```{r import, include=FALSE, cache=TRUE}

dat.res<-read.csv("resistance.runall.csv")

dat.emerg<- read.csv("emerg.runall.csv")

# driveurl<-"https://docs.google.com/spreadsheets/d/1AZJBCdsEjDg2RqNckbHzh9ePkX3dXNtTh1_llMT2l2k/edit#gid=0"
#  
# dat.res<-read_sheet(driveurl, gs4_auth())
# 
# driveurl.2<-"https://docs.google.com/spreadsheets/d/1MSTe9n7sHF9IDK0P-ANJkAtcTTa1-SvusItsbApSIJA/edit#gid=0"
# 
# dat.emerg<-read_sheet(driveurl.2)
# 
# rm(driveurl, driveurl.2)
```

```{r aesthetics}
cbp <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

theme_set(theme_bw())
```

```{r resistance dataset adjustments}
dat.res <- dat.res %>%
  mutate_if(is.character, as.factor) %>%
  mutate_at("rate", as.factor) %>%
  mutate_at("rep", as.factor) %>%
  mutate_at("subsample", as.factor)
# str(dat.res)
# glimpse(dat.res)
```

*metadata for resistance dataset*  
run=experimental run  
rate.L=rate of hydromulch in liters per meter square  
mPa= peak resistance in mPa  
subsample=each hydromulch square was sampled 3 times for peak resistance  
rep=replicate, but since it was a CRD, these do not correspond to any blocking

```{r emergence dataset adjustments}
dat.emerg <- dat.emerg %>%
  mutate_if(is.character, as.factor) %>%
  mutate_at("rate", as.factor) %>%
  mutate_at("rep", as.factor)

dat.emerg %>% 
  str()
```

*metadata for emergence dataset*  
count=number of seeds observed at end of experimental run
count.m2=count on a meter square basis
seed=number of seeds planted in the plot
cum.emerg= % of seeds that emerged through the hydromulch


# RUN ALL CODE ABOVE

```{r}

```


# outlier inspection

```{r outlier inspection}
# outliers are only meaningful within a species and rate

library(lattice)

## dat.emerg
bwplot(cum.emerg ~ factor(rate.L) | run, dat.emerg)
bwplot(cum.emerg ~ factor(rate.L) | species, dat.emerg)
# it seems those two oat data points at 3.2L are extreme

dat.emerg %>%
  rowid_to_column() %>%
  filter(rate.L > 3 & rate.L < 4) %>%
  filter(species == "oat") %>%
  mutate(extreme = is_extreme(.$cum.emerg),
         out = is_outlier(.$cum.emerg)) %>%
  dplyr::select(rowid, out, extreme, cum.emerg, rate.L, species) %>%
  arrange(desc(out)) %>%
  head()
# even though they appear to be outliers, they are not extreme points (see ?is_extreme)


## dat.res
bwplot(mPa ~ factor(rate.L) | run, dat.res)
bwplot(mPa ~ factor(rate.L) | rep, dat.res)
bwplot(mPa ~ factor(rate.L) | subsample, dat.res)
# no big outliers


```

No extreme points were identified, dataset remains unchanged

# summary stats

```{r emergence summary stats}
## all
dat.emerg %>%
  group_by(rate.L) %>%
  summarise(m = mean(cum.emerg),
            se = std.error(cum.emerg))

# making object of summary output
t1 <- dat.emerg %>%
  group_by(rate.L) %>%
  summarise(
    avg.cum.emerg = mean(cum.emerg),
    se = std.error(cum.emerg),
    n = n()
  )
# writing csv that can be copy and pasted from R console in MS word, then use 'text to columns' to turn into a table
write.csv(sapply(t1, function(x)
  round(x, digits = 1)),
  row.names = F)

## by species

dat.emerg %>%
  group_by(rate.L, species) %>%
  summarise(avg.cum.emerg = mean(cum.emerg),
            se = std.error(cum.emerg))

t1 <- dat.emerg %>%
  group_by(rate.L, species) %>%
  summarise(
    avg.cum.emerg = mean(cum.emerg),
    se = std.error(cum.emerg),
    n = n()
  )

write.csv(sapply(t1[, -2], #needed to remove column with species names as it cannot be rounded
                 function(x)
                   round(x, digits = 1)),
          row.names = F) 

```


```{r resistance summary statistics}
## all
dat.res %>%
  group_by(rate.L) %>%
  summarise(avg.dat.res = mean(mPa),
            se = std.error(mPa),
            sd = sd(mPa))

t1 <- dat.res %>%
  group_by(rate.L) %>%
  summarise(
    avg.dat.res = mean(mPa),
    se = std.error(mPa),
    sd = sd(mPa),
    n = n()
  )

write.csv(sapply(t1,
                 function(x)
                   round(x, digits = 2)),
          row.names = F)
```

# emergence

## visualize

Let's see what type of function fits the data best

```{r}

dat.emerg %>%
  ggplot(aes(y = cum.emerg,
             x = rate.L)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = F,
              color = "dodgerblue3") +
  geom_smooth(
    method = "lm",
    formula = y ~ poly(x, 2),
    se = F,
    color = "red"
  ) +
  geom_smooth(method = "loess",
              se = F,
              color = "green") +
  stat_smooth(
    method = "drm",
    method.args = list(fct = LL.4(
  names = c("hill", "min_value", "max_value", "ec_50")
    )),
    se = FALSE,
    color = "purple"
  )
  
```

the purple line fits best, which is the 4 parameter dose response curve

## dose-response model exploration

How many parameters? 
We know the minimum emergence is zero 
We do NOT know the maximum emergence (d-parameter; max asymptope)
We do NOT know the ED50/EC50/LD50 (e parameters; effective dose when 50% of weeds show no emergence)
We do NOT know the slope (b parameter)

3-parameter is most meaningful because we know the minimum emergence is 0, so we define the lower asymptompe. 

We use the log-logistic function. It uses the same parameters as the logistic function (see hill equation). 
More specifically...
c parameter is the lower asymptope
d parameter is the upper asymptope
e parameter is the X-axis value at the inflection point
b parameter is the slope of the curve at the inflection point
see paper 'Gadagkar and Call 2015'


Here is the equation

LL.3== `Y=c+d−c1+(Xe)−b`

Weibull2==`Y=c+(d−c){1−exp{−exp[b(log(X)−log(e))]}}`

Note that simply because Weibull2 is more complex, we will just use the log logistic as it's just as good and simpler.
see https://www.statforbiology.com/2020/stat_nls_usefulfunctions/#weibull-function-type-2



```{r}
dat.emerg %>%
  mutate(species=fct_recode(species,
                        "Barnyardgrass" = "barnyardgrass",
                        "Oat" = "oat",
                        "Pea" = "pea")) %>% 
  # distinct(species)
  ggplot(aes(y = cum.emerg,
             x = rate.L,
             col=species)) +
  geom_point() +
  geom_smooth(
    method = "drm",
    method.args = list(
      fct=LL.4(
        names = c("b",
                  "c",
                  "d",
                  "e")
      )
    ),
    se=F
  ) +
  scale_color_brewer(type = "qual") +
  theme(
    legend.title = element_blank(),
    legend.position = c(.7,.7)
  ) +
  labs(y="Cumulative emergence\n(%)",
       x=expression("Hydromulch rate" ~ (L ~ m^{-2})))

ggsave("emergence.vs.rate.png",
       dpi=400,
       width = 5,
       height = 4,
       units = "in")

```

# resistance



```{r lm fitting}
# we force intercept through the origin since we know there is no resistance at rate.L=0

dat.res %>% 
  # glimpse()
  lm(mPa~0+rate.L,.) %>% 
  summary()

# mPa = rate.L*.132111
# adjusted r2 = 88.3%

```


```{r lm figure}

dat.res %>% 
  ggplot(aes(rate.L,mPa)) +
  stat_summary() +
  stat_smooth(
    method = "lm",
    se=F
  ) +
  annotate(
    geom = "text",
    x=4,
    y=2.5,
    # size=5,
    # label= expression("y=0.132x")
    label = substitute(paste(italic('y = 0.132x')))
  ) +
    annotate(
    geom = "text",
    x=4,
    y=2.2,
    # size=5,
    # label= expression("y=0.132x")
    label = substitute(paste(italic('r2 = 0.88')))
  )

```


```{r final figures}

dat.emerg %>%
  mutate(species=fct_recode(species,
                        "Barnyardgrass" = "barnyardgrass",
                        "Oat" = "oat",
                        "Pea" = "pea")) %>% 
  # distinct(species)
  ggplot(aes(y = cum.emerg,
             x = rate.L,
             col=species)) +
  geom_point() +
  geom_smooth(
    method = "drm",
    method.args = list(
      fct=LL.4(
        names = c("b",
                  "c",
                  "d",
                  "e")
      )
    ),
    se=F
  ) +
  scale_color_brewer(type = "qual") +
  theme(
    legend.title = element_blank(),
    legend.position = c(.7,.7)
  ) +
  labs(y="Emergence (%)",
       x=expression("Hydromulch rate" ~ (L ~ m^{-2}))) -> gg.emerg

dat.res %>% 
  ggplot(aes(rate.L,mPa)) +
  stat_summary(
    fun.data = mean_se
    ) +
  stat_smooth(
    method = "lm",
    se=F,
    formula = y~0+x,
    col = cbp[1]
  ) +
  geom_text(
    aes(x=4,y=2,
        # label = substitute(paste(italic('y = 0.132x'))))
        label = "y = 0.132x\n r2 = 0.88"
  )) +
  labs(y="Resistance (mPa)",
       x="") -> gg.res

# library(ggpubr)
ggpubr::ggarrange(
  gg.res,gg.emerg,
  ncol = 1,
  align = "v"
)

ggsave(
  "fig1.png",
  width = 4,
  height = 6,
  units = "in",
  dpi=500
)


```





